### 2016-01-05 mirror-descent.tex
Very minor fixes

The most prominent instance of \textsc{MD} is \textsc{Projected Gradient
Descent} defined by the recurrence
$$
w_{t+1} = \Pi_K \left( w_t - \eta_t \ell_t \right),
$$
where $\Pi_K(x) = \argmin_{y \in K} \|x-y\|_2$ is the Euclidean projection to
$K$ and $\eta_t > 0$ is the step size.  \textsc{Projected Gradient Descent} is
an instance of \textsc{MD} with regularizer $R_t(w) =
\frac{1}{2\eta_t}\|w\|_2^2$.  A special case of \textsc{Projected Gradient
Descent} with step size $\eta_t = \frac{1}{\sqrt{t}}$ is \textsc{Generalized
Infinitesimal Gradient Ascent} (GIGA)~\cite{Zinkevich-2003}.  Full-matrix and
diagonal versions of \textsc{AdaGrad with Composite MD
Update}~\cite{Duchi-Hazan-Singer-2011} are an instances of \textsc{MD} for any
bounded $K$ with regularizers
$$
R_t(w) = \frac{1}{2} w^\top \left(\sum_{i=1}^t \ell_i \ell_i^\top \right)^{1/2} \!\!\!\! w
\qquad \text{and} \qquad
R_t(w) = \frac{1}{2} \sum_{j=1}^d w_j^2 \sqrt{ \sum_{i=1}^t \ell_{i,j}^2}
$$
respectively. The diagonal version is simply the per-coordinate construction
applied to the one-dimensional version. When $d=1$, both algorithms are
equivalent to
\begin{equation}
\label{equation:ada-grad-regularizer}
R_t(w) = \frac{\|w\|_2^2}{2} \sqrt{\sum_{i=1}^t \|\ell_i\|_2^2 } \; .
\end{equation}
All three sequences of regularizers give a scale-free algorithm. Regularizer
\eqref{equation:ada-grad-regularizer} can be viewed as a scale-free
generalization of GIGA. That is, when $\|\ell_i\|_2
= 1$ for all $i$, \textsc{MD} with regularizer
\eqref{equation:ada-grad-regularizer} coincides with GIGA.

@@

The regret bound for \textsc{Scale-Free MD} in the
Corollary~\ref{corollary:regret-scale-free-mirror-descent} depends on
$\sup_{u,v \in K} \Breg_f(u,v)$. In contrast, the regret bounds for
\textsc{AdaFTRL} and \textsc{SOLO FTRL} in
Corollaries~\ref{corollary:ada-ftrl-regret-bound}~and~\ref{corollary:regret-solo-ftrl-bounded-set}
depend on $\sup_{u \in K} f(u)$.  Similarly, the regret bound in
Theorem~\ref{theorem:regret-scale-free-mirror-descent} for \textsc{Scale-Free
MD} depends on $\sup_{v \in K} \Breg_R(u,v)$ and the regret bounds in
Theorems~\ref{theorem:ada-ftrl-regret-bound}~and~\ref{theorem:regret-solo-ftrl}
for \textsc{AdaFTRL} and \textsc{SOLO FTRL} depend on $R(u)$. It is not hard to
show that
\begin{equation}
\label{equation:regularizer-vs-divergence}
\forall u \in K \qquad R(u) \le \sup_{v \in K} \Breg_R(u,v),
\end{equation}
provided that at the minimizer $v^* = \argmin_{v \in K} R(v)$ both $R(v^*)$ and
$\grad R(v^*)$ are zero. Indeed, in that case, $R(u) = \Breg_R(u,v^*) \le
\sup_{v \in K} \Breg_R(u,v)$.

>>>>

The most prominent instance of \textsc{MD} is \textsc{Projected Gradient
Descent} defined by the recurrence
$$
w_{t+1} = \Pi_K \left( w_t - \eta_t \ell_t \right) \; ,
$$
where $\Pi_K(x) = \argmin_{y \in K} \|x-y\|_2$ is the Euclidean projection to
$K$ and $\eta_t > 0$ is the step size.  \textsc{Projected Gradient Descent} is
an instance of \textsc{MD} with regularizer $R_t(w) =
\frac{1}{2\eta_t}\|w\|_2^2$.  A special case of \textsc{Projected Gradient
Descent} with step size $\eta_t = \frac{1}{\sqrt{t}}$ is \textsc{Generalized
Infinitesimal Gradient Ascent} (GIGA)~\cite{Zinkevich-2003}.  Full-matrix and
diagonal versions of \textsc{AdaGrad with Composite MD
Update}~\cite{Duchi-Hazan-Singer-2011} are an instances of \textsc{MD} for any
bounded $K$ with regularizers
$$
R_t(w) = \frac{1}{2} w^\top \left(\sum_{i=1}^t \ell_i \ell_i^\top \right)^{1/2} \!\!\!\! w
\qquad \text{and} \qquad
R_t(w) = \frac{1}{2} \sum_{j=1}^d w_j^2 \sqrt{ \sum_{i=1}^t \ell_{i,j}^2}
$$
respectively. The diagonal version is simply the per-coordinate construction
applied to the one-dimensional version. When $d=1$, both algorithms are
equivalent to
\begin{equation}
\label{equation:ada-grad-regularizer}
R_t(w) = \frac{\|w\|_2^2}{2} \sqrt{\sum_{i=1}^t \|\ell_i\|_2^2 } \; .
\end{equation}
All three sequences of regularizers give a scale-free algorithm. Regularizer
\eqref{equation:ada-grad-regularizer} can be viewed as a scale-free
generalization of GIGA. That is, when $\|\ell_i\|_2
= 1$ for all $i$, \textsc{MD} with regularizer
\eqref{equation:ada-grad-regularizer} coincides with GIGA.

@@

The regret bound for \textsc{Scale-Free MD} in the
Corollary~\ref{corollary:regret-scale-free-mirror-descent} depends on
$\sup_{u,v \in K} \Breg_f(u,v)$. In contrast, the regret bounds for
\textsc{AdaFTRL} and \textsc{SOLO FTRL} in
Corollaries~\ref{corollary:ada-ftrl-regret-bound}~and~\ref{corollary:regret-solo-ftrl-bounded-set}
depend on $\sup_{u \in K} f(u)$.  Similarly, the regret bound in
Theorem~\ref{theorem:regret-scale-free-mirror-descent} for \textsc{Scale-Free
MD} depends on $\sup_{v \in K} \Breg_R(u,v)$ and the regret bounds in
Theorems~\ref{theorem:ada-ftrl-regret-bound}~and~\ref{theorem:regret-solo-ftrl}
for \textsc{AdaFTRL} and \textsc{SOLO FTRL} depend on $R(u)$. It is not hard to
show that
\begin{equation}
\label{equation:regularizer-vs-divergence}
\forall u \in K \qquad R(u) \le \sup_{v \in K} \Breg_R(u,v) \; ,
\end{equation}
provided that at the minimizer $v^* = \argmin_{v \in K} R(v)$ both $R(v^*)$ and
$\grad R(v^*)$ are zero. Indeed, in that case, $R(u) = \Breg_R(u,v^*) \le
\sup_{v \in K} \Breg_R(u,v)$.
